Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-27 5-Analysis.tex

Like any modeling approaches, these different steps could also be achieved in any order and iteratively. But our goal during the challenge's analysis remains to produce a FML VirtualModels architecture as a federation of VirtualModels. 
As shown in figure~\ref{fig:MultilevelArchitecture}, we defined two VirtualModels (Base and ACME processes abstractions) instantiatied by two VirtualModel instances (XSure and ACME processes). As the figure shows the VirtualModels play the role of metamodels, in the sens of concept definition with a level-blind approach. The VirtualModel instances play the role of models conforms to metamodel definitions. In the rest of the paper, we keep the the vocabulary metamodels and models as to simplify the presentation.
The resulted architecture follows the way the challenge is presented and this organisation allows for the possibility of flexible extensions.

@@

Finally as explained previously, the defined level for the Acme metamodel and the XSure is the result of the instantiation of VirtualModels. In our approach this level can't be specialized or extended but all the other VirtualModels could be extended  by any concepts, as a new federated model. 
Also, the instance level can be instantiated from any VirtualModel, which represent any metamodel level.

>>>>

Like any modeling approaches, these different steps could also be achieved in any order and iteratively. But our goal during the challenge's analysis remains to produce a FML VirtualModels architecture as a federation of VirtualModels. 
As shown in figure~\ref{fig:MultilevelArchitecture}, we defined two VirtualModels (Base and ACME processes abstractions) instantiatied by two VirtualModel instances (XSure and ACME processes). As the figure shows the VirtualModels play the role of metamodels, in the sens of concept definition with a level-blind approach. The VirtualModel instances play the role of models conform to metamodel definitions. In the rest of the paper, we keep the the vocabulary metamodels and models as to simplify the presentation.
The resulted architecture follows the way the challenge is presented and this organisation allows for the possibility of flexible extensions.

@@

Finally as explained previously, the defined level for the Acme  and the XSure models is the result of the instantiation of VirtualModels. In our approach this level can't be specialized or extended but all the other VirtualModels could be extended  by any concepts, as a new federated model. 
Also, the instance level can be instantiated from any VirtualModel, which represent any metamodel level.

### 2021-05-27 7-RequirementsSatisfaction.tex
sync overleaf->github

Now we discuss how the solution satisfies the challenge requirements.

@@

Sylvain

>>>>

%Satisfaction of Requirements: demonstration of how the solution satisfies the challenge requirements

In the previous section~\ref{sec:model}, we demonstrated that our solution satisfies all the challenge requirements. In this section, we summarize the different techniques used to satisfy them, without repeating all the justifications.

%Now we discuss how the solution satisfies the challenge requirements.

@@

\todo[inline]{OK pour le tableau synthétique +un petit peu de texte + une mini intro qui référence la section précédente (vu que les req ont été couverts dans la section précédente ; pas de fusion des deux sections}

\begin{tabular}{|l|c|r|}
   \hline
   colonne 1 & \multicolumn{2}{c|}{colonnes 2 et 3} \\
   \hline
   1.1 & 1.2 & 1.3 \\
   \hline
   2.1 & 2.2 & \checkmark \\
   \hline
\end{tabular}
